Technique for \earlywarning\ detection of compact binary coalescence and its implication for multi-messenger astronomy

### 2011-06-02 analysis.tex
Added template placement plot
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@841 ccdd05d5-56c1-461a-bf98-85f6876523b4

>>>>

\begin{figure}[htbp]
	\label{fig:tmpltbank}
	\begin{center}
		\includegraphics[scale=0.75]{figures/tmpltbank.png}
		\caption{Placement of template parameters used in this paper.  The template bank consists of 98544 templates with component masses $m_1$, $m_2$, between 1~and~3~$M_\odot$.  We shall design a filter bank to search for a small subset of these template parameters with chirp masses $\mathcal M$ between 1.1955~and~1.2045~$M_\odot$.}
	\end{center}
\end{figure}
